\documentclass[a4paper,openany,twocolumn]{book}

\usepackage{fontspec}
\usepackage[justified]{dnd}
\usepackage{ifthen}
\usepackage{pstricks}

\usepackage[UKenglish]{babel}

\input{../character-sheet-settings}
\input{../template/character-sheet-commands}

\newcommand{\name}{}


% Headline
\CharacterName{\name}

\Class{Druid 1}
\Background{Sage}
\PlayerName{Skye}
\Race{Tabaxi}
\Alignment{Chaotic Neutral}
\XP{0}

% Dice rolls
% 3 6 6   = 15
% 3 5 3   = 11
% 3 5 6   = 14
% 3 4 5   = 12
% 4 5 5   = 14
% 5 4 4   = 13

% Ability scores
\StrengthScore{12}
\DexterityScore{16} % + 2 tabaxi
\ConstitutionScore{13}
\IntelligenceScore{14}
\WisdomScore{15}
\CharismaScore{7} % + 1 tabaxi

% Ability modifiers
\StrengthModifier{+1}
\DexterityModifier{+3}
\ConstitutionModifier{+1}
\IntelligenceModifier{+2}
\WisdomModifier{+2}
\CharismaModifier{-2}

% Saving Throws
\StrengthSavingThrowModifier{+1}
\DexteritySavingThrowModifier{+3}
\ConstitutionSavingThrowModifier{+1}
\IntelligenceSavingThrowModifier{+4} % Prof
\WisdomSavingThrowModifier{+4} % Prof
\CharismaSavingThrowModifier{+1}

\AcrobaticsSkillModifier{+3}
\AnimalHandlingSkillModifier{+4}
\ArcanaSkillModifier{+2}
\AthleticsSkillModifier{+1}
\DeceptionSkillModifier{+1}
\HistorySkillModifier{+2}
\InsightSkillModifier{+2}
\IntimidationSkillModifier{+1}
\InvestigationSkillModifier{+2}
\MedicineSkillModifier{+2}
\NatureSkillModifier{+4}
\PerceptionSkillModifier{+4}
\PerformanceSkillModifier{+1}
\PersuasionSkillModifier{+1}
\ReligionSkillModifier{+2}
\SleightOfHandSkillModifier{+3}
\StealthSkillModifier{+3}
\SurvivalSkillModifier{+2}

% Proficiencies
\StrengthProficiency{}
\DexterityProficiency{}
\ConstitutionProficiency{}
\IntelligenceProficiency{True}
\WisdomProficiency{True}
\CharismaProficiency{}

\AcrobaticsProficiency{}
\AnimalHandlingProficiency{True} % Druid
\ArcanaProficiency{True} % Sage
\AthleticsProficiency{}
\DeceptionProficiency{}
\HistoryProficiency{True} % Sage
\InsightProficiency{}
\IntimidationProficiency{}
\InvestigationProficiency{}
\MedicineProficiency{}
\NatureProficiency{True} % Druid
\PerceptionProficiency{True} % Tabaxi
\PerformanceProficiency{}
\PersuasionProficiency{}
\ReligionProficiency{}
\SleightOfHandProficiency{}
\StealthProficiency{True} % Tabaxi

\Inspiration{}
\Proficiency{+2}
\Perception{17} %+5 Observant

\ArmorClass{14}
\Initiative{0}
\Speed{30ft}
\MaxHitPoints{9}
\CurrentHitPoints{9}
\TemporaryHitPoints{}
\MaxHitDice{1d8}
\CurrentHitDice{1d8}

\CP{}
\SP{}
\GP{10}
\EP{}
\PP{}


\AddWeapon{Scimitar}{+5}{1d6 + 3 s}
\AddWeapon{Dart}{+5 (range 20/60)}{1d4 +5 p}

\AttacksAdditional{
  \textbf{Druidic Focus:}\\A wand made from a branch of a small tree \name
  nurtured since childhood.\\
}

\OtherProficienciesLanguages{
\textbf{Languages:}\\Common, Druidic, Sylvan\\
\textbf{Armor:}\\Light Armor, Medium Armor\\
\textbf{Weapons:}\\Clubs, Daggers, Darts, Javelins, Maces, Quarterstaff,
Scimitars, Sickles, Slings, Spears\\
\textbf{Tools:}\\Herbalism  tools
}

\Equipment{
  Leather Armor,
  Explorer's Pack,
  Darts,
  Druidic Focus,
  A bottle of black ink,
  A quill,
  A small knife,
  Letter from a dead colleague,
  Common Clothes
}

\PersonalityTraits{
  \begin{itemize}
    \item Shy due to not spending much time with others, but easily excited
          by topics she is interested (primarily animals and nature).
    \item Despite her interest in sea life, she's terrified of water and will
          not get near it.
  \end{itemize}
}

\Ideals{
  She believes nature is incredibly precious, and seeks to understand how best
  she and humanity in general can fit into it.
}

\Bonds{
  \begin{itemize}
    \item She had an Elven friend in college named Shara, who seemed to be on
          the verge of some understanding, before she mysteriously disappeared.
  \end{itemize}
}

\Flaws{
  \begin{itemize}
    \item Likely to prioritize her own interests over what might be better for
          those around her.
    \item Not well socialized, and often will speak out or ignore politeness.
  \end{itemize}
}

\FeaturesTraits{
\textbf{Tabaxi}
\begin{itemize}
  \item Darkvision
  \item Feline Agility
  \item Cat's Claws
\end{itemize}
\textbf{Druid}
\begin{itemize}
  \item Spell Casting
  \item Ritual Casting
\end{itemize}
\textbf{Sage}
\begin{itemize}
        \item Researcher
\end{itemize}
}


% Magic

\SpellcastingClass{Druid}
\SpellcastingAbility{WIS}
\SpellSaveDC{12}
\SpellAttackBonus{+4}

\CantripSlotA{Druidcraft (V, S)}
\CantripSlotB{Thorn Whip (V, S, M)}

\FirstLevelSpellSlotsTotal{2}
\FirstLevelSpellSlotA{Animal Friendship}
\FirstLevelSpellSlotB{Cure Wounds}
\FirstLevelSpellSlotC{Goodberry}


\begin{document}
\newgeometry{left=0cm,right=0cm,top=0cm,bottom=0cm}
\onecolumn


% CHARACTER PAGE
\input{../template/character-sheet.tex}

% SPELLCASTING PAGE
\input{../template/spell-sheet.tex}


\restoregeometry
\twocolumn

\chapter*{Features, Magic Items and Spells}

\section*{Tabaxi}
\subsection{Darkvision}
You have a cat's keen senses, especially in the dark. You can see in dim light
within 60 feet of you as if it were bright light, and in darkness as if it were
dim light. You can't discern color in darkness, only shades of gray.
\subsection{Feline Agility}
Your reflexes and agility allow you to
move with a burst of speed. When you move on your
tum in combat, you can double your speed until the end
of the tum. Once you use this trait, you can't use it again
until you move O feet on one of your turns.
\subsection{Cat's Claws}
Because of your claws, you have a climbing speed of 20 feet. In addition, your
claws are natural weapons, which you can use to make unarmed strikes.  If you
hit with them, you deal slashing damage equal to 1d4 + your Strength modifier,
instead of the bludgeoning damage normal for an unarmed strike.
\subsection{Cat's Talent}
You have proficiency in the Perception and Stealth skills.
\section*{Druid}
\subsection*{Druidic}
You know Druidic, the secret language of druids. You can speak the language and
use it to leave hidden messages. You and others who know this language
automatically spot such a message. Others spot the message's presence with a
successful DC 15 Wisdom (Perception) check but can't decipher it without magic.
\subsection*{Ritual Casting}
You can cast a druid spell as a ritual if that spell has the ritual tag and you
have the spell prepared.

\section*{Background}
\subsection*{Sage}
You understand wealth, power, and privilege. You carry a noble title, and your family owns land, collects taxes, and wields significant political influence.

You come from an established family in another land to the north, and have been outcast as you are the only member of your family to display sorcerous trait, and seek adventure to discover more about this element of your being.

\subparagraph*{Skill Proficiencies} Arcana, History
\subparagraph*{Languages} Two of your choice
\subparagraph*{Equipment}  A bottle of black ink, a quill, a small knife, a
letter from a dead colleague posing a question you have not yet been able to
answer, a set of common clothes, and a pouch containing 10 gp


\subsubsection*{Researcher}
When you attempt to learn or recall a piece of lore, if you do not know that
information, you often know where and from whom you can obtain it. Usually, this
information comes from a library, scriptorium, university, or a sage or other
learned person or creature. Your DM might rule that the knowledge you seek is
secreted away in an almost inaccessible place, or that it simply cannot be
found. Unearthing the deepest secrets of the multiverse can require an adventure
or even a whole campaign.


\section*{Spells}
\subsection*{Cantrips}

\DndSpellHeader
{Druidcraft}
{Transmutation Cantrip}
{1 Action}
{30 Feet}
{V, S}
{Instantaneous}

Whispering to the spirits of nature, you create one of the
following effects within range:


\begin{itemize}
  \item You create a tiny, harmless sensory effect that predicts what the
weather will be at your location for the next 24 hours. The effect might
manifest as a golden orb for clear skies, a cloud for rain, falling snowflakes
for snow, and so on. This effect persists for 1 round.
  \item You instantly make a flower blossom, a seed pod open, or a leaf bud
bloom.
  \item You create an instantaneous, harmless sensory effect, such as falling
leaves, a puff of wind, the sound of a small animal, or the faint odor of skunk.
The effect must fit in a 5-foot cube.
  \item You instantly light or snuff out a candle, a torch, or a
small campfire.
\end{itemize}

\DndSpellHeader
{Thorn Whip}
{Transmutation Cantrip}
{1 Action}
{3 feet}
{V, S, M (the stem of a plant with thorns)}
{Instantaneous}

You create a long, vine-like whip covered in thorns that lashes out at your
command toward a creature in range.  Make a melee spell attack against the
target. If the attack hits, the creature takes 1d6 piercing damage, and if the
creature is Large or smaller, you pull the creature up to 10 feet closer to you.

This spell's damage increases by 1d6 when you reach 5th level (2d6), 11th level
(3d6), and 17th level (4d6).

\end{document}

% Local Variables:
% TeX-engine: xetex
% End:

